CdGF_aucrf

### 2016-10-14 code/HumanCdGF_microbiota_strains.Rmd
fix median and axis label

```{r fig.height= 5, fig.width=10}
non_431 %>% 
  filter(day %in% c(0:10), !is.na(log_cfu) ) %>%
  select(mouse_id, day, human_source, cdiff_strain, cage_id, log_cfu) %>% 
  ggplot(aes(x = factor(day), y = log_cfu, color = factor(cdiff_strain))) + geom_point() +
            stat_summary(fun.y=mean, geom="line", aes(group = cage_id)) + 
            facet_grid(. ~ human_source) + theme_bw() + 
            labs(x = 'Day', y = 'C Diff CFU (log10)') +
            theme(legend.justification=c(1,0.5), legend.position=c(1,0.5), 
                  legend.title=element_blank())

```

>>>>

```{r fig.height= 5, fig.width=10}
non_431 %>% 
  filter(day %in% c(0:10), !is.na(log_cfu) ) %>%
  select(mouse_id, day, human_source, cdiff_strain, cage_id, log_cfu) %>% 
  ggplot(aes(x = factor(day), y = log_cfu, color = factor(cdiff_strain))) + geom_point() +
            stat_summary(fun.y=median, geom="line", aes(group = cage_id)) + 
            facet_grid(. ~ human_source) + theme_bw() + 
            labs(x = 'Day', y = expression(paste(italic('C. Difficile'), ' Log'[10], ' CFU', sep = ''))) +
            theme(legend.justification=c(1,0.5), legend.position=c(1,0.5), 
                  legend.title=element_blank())
```
